Visually pleasing knot projections

### 2022-06-09 inst/jma_rebuttal_review3.tex

{The above two comments suggest, that it might be advantageous to use
  some hierarchy in the representation of symmetrical knots: Only
  specify the curve for one unique fragment of the knot curve, and
  compose the complete curve by instancing that fragment with
  mirroring and rotation as required to construct the complete knot!
  The optimization would then only have to be done for this unique
  fragment (with proper end-conditions).  If this same hierarchy is
  also used in the graphical display of the knot curve, the user could
  easily make adjustments to just a few nodes, while always
  automatically obtaining the desired symmetrical result.}

\textcolor{blue}{This is exactly what I have done!  The referee gives
  an accurate summary of the code's methodology.\\ \\}

Page 10 lines 55: ``In the package, the badness weightings may be
altered easily,..."  -- What is the user interface for this?  Are
there sliders in the display that allow interactive adjustments of the
weights?

\textcolor{blue}{I have not implemented sliders.  The weightings may
  be changed in function {\tt badness()}, and documentation (including
  examples) is given at {\tt badness.Rd}.\\ \\}

@@

Figure 9: The fact that ``angle-crossing penalty" had to be enhanced by
a factor of 100 to achieve a more desirable (in my opinion) result,
illustrates the fact that the "total crossing angles()"-function is
not a good choice for optimization.

\textcolor{blue}{As discussed above, {\tt total\_crossing\_angles()}
  was a somewhat misleading name.  The factor of 100 ensured that even
  tiny deviations from exactly $90^\circ$ were heavily penalised.}

### 2022-06-09 inst/jma_rebuttal_review3.tex

Why not use some other spline curve that guarantees G2-continuity?

\textcolor{blue}{I don't have a good answer to that, other than to
  point out that the focus of the manuscript was to investigate the
  visual appearance of knots using mathematical optimization routines.
  I do not wish to rule out using other G2-continuous splines, and it
  might be interesting some day to consider (e.g.) B-splines.  But as
  I say above, Bezier curves are a good starting point.}

And, if forced by the chosen tool to use Bezier curves, why not place
nodes at the crossing points, (and one or two more for large loopy
lobes between subsequent crossing points)?  -- This would allow the
user to place the crossing points far enough apart to start with, and
this would make it easy to set the Bezier handles to force right-angle
crossings.

\textcolor{blue}{Most of this issue is discussed below, at the comment
  for page 4, lines 53-54.  But here I would observe that it is not at
  all easy to manipulate Bezier handles on two distinct nodes [which
    happen to coincide spatially] to result in their two respective
  lines being orthogonal.  Observe that the overstrand and understrand
  of a crossing point may have (for good reasons!) very different
  curvatures.}

### 2022-06-09 inst/jma_knot.tex
fixes #61

\begin{figure}[!tbp]
\begin{verbatim}
knotplot2(k7_6,text=TRUE,lwd=1,circ=0,rainbow=TRUE)
\end{verbatim}
 \centering
\includegraphics[scale = 0.9]{knot-004}
\caption{Knot~$7_6$ with strands numbered \label{k76_strands} so that
  the sense of the crossings can be established.  For example, strand
  7 passes over strand 3.  In the package, this fact is specified by
  the {\tt overunder} object, as discussed in the text, having a row
  {\tt 7 3} (and not {\tt 3 7} which would be the crossing having the
  opposite sense)} \end{figure}

>>>>

\begin{figure}[!tbp]
\begin{verbatim}
knotplot2(k7_6,text=TRUE,lwd=1,circ=0,rainbow=TRUE)
\end{verbatim}
 \centering
\includegraphics[scale = 0.9]{knot-004}
\caption{Knot~$7_6$ with strands numbered \label{k76_strands} so that
  the sense of the crossings can be established.  For example, strand
  7 passes over strand 3.  In the package, this fact is specified by
  the {\tt overunder} object, as discussed in the text, having a row
  {\tt 7 3} (and not {\tt 3 7} which would be the crossing having the
  opposite sense).  Crossings become relevant only for the final
  rendering of the knot curve with the gaps included}
\end{figure}
